NumPy---Array Programming in Python

### 2020-02-21 body.tex
Minor edits
Fix word

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{NumPy is the base of the scientific Python ecosystem.}
   Essential libraries and projects that depend on NumPy's API gain access to new array
   implementations that support NumPy's array protocols (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}

@@

SciPy and Matplotlib are tightly coupled with NumPy---in terms of
history, development, and use.
SciPy provides fundamental algorithms for scientific computing,
including mathematical, scientific, and engineering routines.
Matplotlib generates publication-ready figures and visualizations.
The combination of NumPy, SciPy, and Matplotlib, together with
an advanced interactive environment like IPython \cite{perez2007ipython},
or Jupyter \cite{Kluyver:2016aa}, provides a solid foundation for array
programming in Python.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this foundation to provide several, widely used \emph{technique specific}
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
that in turn underlay numerous \emph{domain specific} projects
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,sunpy2015,2018EGUGA..2012146H}.
NumPy, at the root of the ecosystem of array-aware libraries,
sets documentation standards, provides array testing infrastructure,
and adds build support for Fortran and other compilers.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{NumPy is the base of the scientific Python ecosystem.}
   Essential libraries and projects that depend on NumPy's API gain access to new array
   implementations that support NumPy's array protocols (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}

@@

SciPy and Matplotlib are tightly coupled with NumPy---in terms of
history, development, and use.
SciPy provides fundamental algorithms for scientific computing,
including mathematical, scientific, and engineering routines.
Matplotlib generates publication-ready figures and visualizations.
The combination of NumPy, SciPy, and Matplotlib, together with
an advanced interactive environment like IPython \cite{perez2007ipython},
or Jupyter \cite{Kluyver:2016aa}, provides a solid foundation for array
programming in Python.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this foundation to provide several, widely used \emph{technique specific}
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
that in turn underlay numerous \emph{domain specific} projects
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,sunpy2015,2018EGUGA..2012146H}.
NumPy, at the base of the ecosystem of array-aware libraries,
sets documentation standards, provides array testing infrastructure,
and adds build support for Fortran and other compilers.
